---
title: "Final"
author: "Sylvie Prepetit"
format: html
editor: visual
execute:
  Echo: false 
---
The data set consists of various variables including the company location, country of bean origin, cocoa percentage, ingredients, and rating. It is sourced from the \*\*Tidytuesday project\*\* and was specifically obtained from the 2022-01-18 dataset. I am exploring the distribution of ratings, performing a regression analysis, and summarizing key statistics.

```{r, load-data, echo= FALSE}
#Load libraries and data set 
library(gtsummary)
library(tidyverse)
library(tidytuesdayR)
library(dplyr)
library(forcats)

# Get the data?

tuesdata <- tidytuesdayR::tt_load('2022-01-18')
chocolate <- tuesdata$chocolate

```

```{r, group-data}
#| echo: false
#Grouping my categories of interest
chocolate2 <- chocolate|>
  mutate(company_location2 = fct_lump(company_location, n = 3),
  			 bean_origin2 = fct_lump(country_of_bean_origin, n = 5),
  			 cocoa_pct2 = fct_lump(cocoa_percent, n = 5),
				 ingredients2 = fct_lump(ingredients, n = 3)
	)

# Ensure the 'data' directory exists
dir.create(here::here("data"), showWarnings = FALSE, recursive = TRUE)

# Save the grouped data to a CSV file
write_csv(chocolate2, here::here("data", "chocolate_grouped.csv"))

```

```{r, creating-table}
#| label: tbl-one
#| tbl-cap: "This is a table"
  tbl_summary(
  	chocolate2,
  	by=company_location2,
  	include = c( bean_origin2, cocoa_pct2, ingredients2),
  	missing_text = "missing")  |>

  	add_overall()|>
    bold_labels()
```
@tbl-one contains a table
```{r, regression-model}
    tbl_uvregression(
  	chocolate2,
  	y = rating,
  	include = c(bean_origin2, cocoa_pct2,ingredients2),
  	method = glm,
  	method.args=list(family = gaussian()))
 
```

```{r, hist}
#| label: fig-hist
#| fig-cap: "This is a histogram"
hist(chocolate2$rating)
ggsave(here::here("figure","fig.hist.png"))
```
@fig-one contains a figure 
```{r, create-function}
 new_mean <- function(x) {
	n <- length(x)
	mean_val <- sum(x) / n
	return(mean_val)
 }

 new_mean(chocolate2$rating)

 # function for standard deviation 
 new_sd <- function(x) {
 	n <- length(x)
 	mean_val <- sum(x) / n
 	squared_diff <- (x - mean_val)^2
 	variance <- sum(squared_diff) / (n - 1)
 	sd_val <- sqrt(variance)
 	return(sd_val)
 }

 new_sd(chocolate2$rating)
```


The standard deviation for the chocolate ratings is `r new_sd(chocolate2$rating)`
